---
title: "Supplementary Material 2"
subtitle: "Mathematical Formulas and parameters used in SS3 for Krill Stock Assessment"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: bib/SA_krill.bib
csl: bib/apa.csl
link-citations: yes
linkcolor: blue
output:
  bookdown::pdf_document2:
    keep_md: false
    toc: false
    number_sections: false
    fontsize: 11pt
    linestretch: 1.5
    latex_engine: xelatex
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
always_allow_html: true
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r libs, echo=FALSE, message=FALSE, warning=FALSE}
library(here)
library(r4ss)
library(dplyr)
library(kableExtra)

kbl_pdf <- function(x, caption = NULL, scale = TRUE, font = 9, ...) {
  opts <- c("HOLD_position", if (scale) "scale_down")
  kbl(x, booktabs = TRUE, format = "latex", caption = caption, ...) %>%
    kable_styling(latex_options = opts, font_size = font, full_width = FALSE)
}
```

\newpage

# Main equations

## State Model

**Population Dynamics**

\begin{equation}
N_{a,l,s,t+1} = N_{a-1,l,s,t} \cdot e^{-(M_{a-1,l,s,t} + F_{a-1,l,s,t})} \cdot T_{a-1 \to a,l,s,t} + R_{a,l,s,t}
\end{equation}

**Total Mortality**

\begin{equation}
Z_{a,l,s,t} = M_{a,l,s,t} + F_{a,l,s,t}
\end{equation}

**Spawning Stock Biomass**

\begin{equation}
SSB_t = \sum_a \sum_l \sum_s N_{a,l,s,t} \cdot W_{a,l,s,t} \cdot \text{Mat}_{a,l,s,t} \cdot \text{Fec}_{a,l,s,t}
\end{equation}

**Total Biomass**

\begin{equation}
B_t = \sum_a \sum_l \sum_s N_{a,l,s,t} \cdot W_{a,l,s,t}
\end{equation}

## Sub-models

**Selectivity**

\begin{equation}
S_{a,l,f} = \frac{1}{1 + e^{-\ln(19) \cdot \frac{L_l - L_{50,f}}{L_{95,f} - L_{50,f}}}}
\end{equation}

\begin{equation}
S_{a,f,t} = \sum_l S_{l,f,t} \cdot P(L_l \mid a, t)
\end{equation}

**Stock-Recruitment**

\begin{equation}
R_t = \frac{\alpha \cdot SSB_{t-\tau}}{\beta + SSB_{t-\tau}} \cdot e^{\delta_t - \frac{\sigma^2_R}{2}}
\end{equation}

**Environmental Effects on Recruitment**

\begin{equation}
E(\text{Recruitment}) = f(SSB) \times \exp(B \times \text{env}) \times \exp\!\left(-0.5 \times \pi^2_R\right)
\end{equation}

**Maturity**

\begin{equation}
\text{Mat}_l = \frac{1}{1 + e^{-\ln(19) \cdot \frac{L_l - L_{50}}{L_{95} - L_{50}}}}
\end{equation}

\begin{equation}
\text{Mat}_{a,t} = \sum_l \text{Mat}_l \cdot P(L_l \mid a, t)
\end{equation}

**Growth (Von Bertalanffy)**

\begin{equation}
L_{a,s} = L_{\infty,s} \cdot \left(1 - e^{-K_s \cdot (a - t_{0,s})}\right)
\end{equation}

**Weight-Length Relationship**

\begin{equation}
W_{l,s} = w_s \cdot L^{b_s}_l
\end{equation}

**Length-at-Age Variability**

\begin{equation}
P(L_l \mid a, s, t) = \frac{1}{\sqrt{2\pi}\,\sigma_{L|a,s}} \exp\!\left(-\frac{(L_l - \bar{L}_{a,s,t})^2}{2\sigma^2_{L|a,s}}\right)
\end{equation}

**Length-to-Age Transition Matrix**

\begin{equation}
T_{a,l \to a+1,l',s,t} = P(L_{l'} \mid a+1, s, t+1) \cdot \text{Growth}_{l \to l'}
\end{equation}

The ALK matrix is typically defined as:

\begin{equation}
P(A = a \mid L = l) = \frac{N_{a,l}}{\sum_a N_{a,l}}
\end{equation}

where $P(A = a \mid L = l)$ is the probability that an individual of length $l$ belongs to age $a$, $N_{a,l}$ is the number of individuals of age $a$ observed at length $l$, and the denominator $\sum_a N_{a,l}$ ensures that the probabilities sum to 1 for each length class. This matrix is then used in the model to allocate observed length compositions into age classes:

\begin{equation}
N_a = \sum_l P(A = a \mid L = l) \cdot N_l
\end{equation}

where $N_l$ is the number of fish observed at length $l$, and $N_a$ is the estimated number at age.

**Fishing Mortality**

\begin{equation}
F_{a,l,s,f,t} = F'_{f,t} \cdot S_{a,l,s,f,t}
\end{equation}

\begin{equation}
F_{a,l,s,t} = \sum_f F_{a,l,s,f,t}
\end{equation}

**Predator Mortality**

\begin{equation}
M_{a,t} = M1_{a,t} + M2_{a,t}
\end{equation}

\begin{equation}
M2_{a,t} = \sum_{p=1}^{n_\text{pred}} \frac{C_{p,t} \cdot S_{p,a}}{B_{\text{avail},t}}
\end{equation}

## Catch Equations

\begin{equation}
C_{a,l,s,f,t} = \frac{F_{a,l,s,f,t}}{Z_{a,l,s,t}} \cdot N_{a,l,s,t} \cdot \left(1 - e^{-Z_{a,l,s,t}}\right) \cdot W_{a,l,s,t}
\end{equation}

\begin{equation}
C_{f,t} = \sum_a \sum_l \sum_s C_{a,l,s,f,t}
\end{equation}

## Observation Model

\begin{equation}
\hat{I}_{q,t} = Q_q \cdot \sum_a \sum_l \sum_s N_{a,l,s,t} \cdot S_{a,l,s,q,t} \cdot W_{a,l,s,t}
\end{equation}

\begin{equation}
\hat{P}_{a,f,t} = \frac{C_{a,f,t}}{\sum_a C_{a,f,t}}
\end{equation}

\begin{equation}
\hat{P}_{l,f,t} = \frac{\sum_a C_{a,l,f,t}}{\sum_a \sum_l C_{a,l,f,t}}
\end{equation}

## Likelihood Components

\begin{equation}
\mathcal{L}_\text{survey} = -\sum_q \sum_t \frac{1}{2} \left[\frac{(\ln I_{q,t} - \ln \hat{I}_{q,t})^2}{\sigma^2_{I,q}} + \ln(2\pi\sigma^2_{I,q})\right]
\end{equation}

\begin{equation}
\mathcal{L}_\text{age} = -\sum_f \sum_t N_{\text{eff},f,t} \sum_a P_{a,f,t} \ln \hat{P}_{a,f,t}
\end{equation}

\begin{equation}
\mathcal{L}_\text{length} = -\sum_f \sum_t N_{\text{eff},f,t} \sum_l P_{l,f,t} \ln \hat{P}_{l,f,t}
\end{equation}

\begin{equation}
\mathcal{L}_\text{rec} = -\frac{1}{2}\left[\sum_t \frac{\delta^2_t}{\sigma^2_R} + \ln(2\pi\sigma^2_R)\right]
\end{equation}

## Parameter Estimation

\begin{equation}
-\ln(\mathcal{L}_\text{total}) = -\sum_i w_i \ln(\mathcal{L}_i)
\end{equation}

\begin{equation}
\text{Penalty} = \lambda \sum_j \left(\frac{\theta_j - \theta_{j,\text{prior}}}{\sigma_{\theta,j}}\right)^2
\end{equation}

\newpage

# Model Parameter Configuration

The following table summarizes the key parameters used to condition the reference model, including biological, growth, and population dynamics factors (Table \@ref(tab:parainit1)).

```{r parainit1, eval=TRUE}
dir1.1 <- here("s1.1")
start1 <- SS_readstarter(file = file.path(dir1.1, "starter.ss"), verbose = FALSE)
dat1   <- SS_readdat(file = file.path(dir1.1, start1$datfile), verbose = FALSE)
ctl1   <- SS_readctl(file = file.path(dir1.1, start1$ctlfil),
                     verbose = FALSE, use_datlist = TRUE, datlist = dat1)
fore1  <- SS_readforecast(file = file.path(dir1.1, "forecast.ss"), verbose = FALSE)

# Extraer parámetros
parbio <- ctl1$MG_parms[1:10, c(1:4,7)]
rownames(parbio) <- c("Nat M", "Lmin", "Lmax", "VonBert K",
                      "CV young", "CV old", "Wt a", "Wt b", "L50%", "Mat slope")
SRpar  <- ctl1$SR_parms[1:5, c(1:4,7)]
Qpar   <- ctl1$Q_parms[1:2, c(1:4,7)]
Selpar <- ctl1$size_selex_parms[1:20, c(1:4,7)]

# Combinar parámetros
parInit <- as.data.frame(rbind(parbio, SRpar, Qpar, Selpar))
parInit$Parameter <- rownames(parInit)

# Añadir categorías y reordenar columnas
categories <- c(rep("Natural Mortality", 1),
                rep("Growth", 4),
                rep("Length-Weight Relation", 2),
                rep("Maturity", 2),
                rep("CV young/old", 1),
                rep("Stock-Recruit Relation", 5),
                rep("Catchability", 2),
                rep("Selectivity", 20))

parInit <- parInit %>%
  mutate(INIT  = round(INIT, 2),
         PRIOR = round(PRIOR, 2),
         Category = categories) %>%
  dplyr::relocate(Category, Parameter)

kbl_pdf(parInit, font = 8,
        caption = "Input parameters for the initial SS3 model of krill. Each parameter line contains a minimum value (LO), maximum value (HI), and initial value (INIT). If the phase (PHASE) for the parameter is negative, the parameter is fixed as input.")
```


\newpage

# Glossary of Terms and Parameters

```{r glossary, echo=FALSE}
library(kableExtra)

glossary <- data.frame(
  Symbol = c(
    "$N_{a,l,s,t}$", "$M_{a,l,s,t}$", "$F_{a,l,s,t}$", "$Z_{a,l,s,t}$",
    "$R_t$", "$SSB_t$", "$B_t$", "$W_{a,l,s,t}$", "$\\text{Mat}_{a,l,s,t}$",
    "$\\text{Fec}_{a,l,s,t}$", "$S_{a,l,f}$", "$L_{\\infty,s}$", "$K_s$",
    "$t_{0,s}$", "$w_s$", "$b_s$", "$L_{50}$", "$L_{95}$",
    "$L_{50,f}$", "$L_{95,f}$", "$\\alpha$", "$\\beta$",
    "$\\sigma_R$", "$\\delta_t$", "$Q_q$", "$C_{a,l,s,f,t}$",
    "$I_{q,t}$", "$\\hat{I}_{q,t}$", "$P_{a,f,t}$", "$\\hat{P}_{a,f,t}$",
    "$P_{l,f,t}$", "$\\hat{P}_{l,f,t}$", "$N_{\\text{eff},f,t}$",
    "$\\sigma_{I,q}$", "$M1_{a,t}$", "$M2_{a,t}$", "$C_{p,t}$",
    "$S_{p,a}$", "$B_{\\text{avail},t}$", "$\\beta_i$", "$X_{i,t}$",
    "$\\lambda$", "$w_i$", "$\\theta_j$", "$\\theta_{j,\\text{prior}}$",
    "$\\sigma_{\\theta,j}$", "$\\tau$", "$F'_{f,t}$", "$R_0$", "$h$"
  ),
  Description = c(
    "Number of individuals at age $a$, length $l$, sex $s$, time $t$",
    "Natural mortality rate", "Fishing mortality rate", "Total mortality rate",
    "Recruitment at time $t$", "Spawning stock biomass at time $t$",
    "Total biomass at time $t$", "Weight-at-age-length-sex",
    "Proportion mature at age-length-sex", "Fecundity-at-age-length-sex",
    "Selectivity for fleet $f$ at age $a$, length $l$",
    "Asymptotic length for sex $s$", "Growth rate parameter for sex $s$",
    "Theoretical age at length zero for sex $s$",
    "Weight-length scaling parameter for sex $s$",
    "Weight-length allometric exponent for sex $s$",
    "Length at 50\\% maturity", "Length at 95\\% maturity",
    "Length at 50\\% selectivity for fleet $f$",
    "Length at 95\\% selectivity for fleet $f$",
    "Stock-recruitment steepness parameter",
    "Stock-recruitment capacity parameter",
    "Recruitment variability", "Recruitment deviation in year $t$",
    "Catchability coefficient for survey $q$",
    "Catch at age-length-sex by fleet $f$ at time $t$",
    "Observed survey index for survey $q$ at time $t$",
    "Expected survey index for survey $q$ at time $t$",
    "Observed age composition for fleet $f$ at time $t$",
    "Expected age composition for fleet $f$ at time $t$",
    "Observed length composition for fleet $f$ at time $t$",
    "Expected length composition for fleet $f$ at time $t$",
    "Effective sample size for fleet $f$ at time $t$",
    "Standard deviation of survey index $q$",
    "Base natural mortality at age $a$, time $t$",
    "Predation mortality at age $a$, time $t$",
    "Consumption by predator $p$ at time $t$",
    "Age-specific selectivity by predator $p$",
    "Available biomass for predation at time $t$",
    "Environmental coefficient for covariate $i$",
    "Environmental covariate $i$ at time $t$",
    "Penalty weight", "Likelihood component weight",
    "Estimated parameter $j$", "Prior mean for parameter $j$",
    "Prior standard deviation for parameter $j$",
    "Recruitment lag (spawning to recruitment age)",
    "Fully-selected fishing mortality for fleet $f$",
    "Unfished recruitment level",
    "Steepness parameter in stock-recruitment"
  ),
  Units = c(
    "Thousands", "yr$^{-1}$", "yr$^{-1}$", "yr$^{-1}$",
    "Thousands", "Metric tons", "Metric tons", "Grams",
    "Proportion", "Eggs/individual", "Proportion",
    "mm", "yr$^{-1}$", "Years", "g/mm$^b$", "Dimensionless",
    "mm", "mm", "mm", "mm",
    "Various", "Various", "Dimensionless", "Log-scale",
    "Various", "Metric tons", "Various", "Various",
    "Proportion", "Proportion", "Proportion", "Proportion",
    "Dimensionless", "Log-scale", "yr$^{-1}$", "yr$^{-1}$",
    "Metric tons", "Proportion", "Metric tons",
    "Dimensionless", "Various", "Dimensionless", "Dimensionless",
    "Various", "Various", "Various", "Years",
    "yr$^{-1}$", "Thousands", "Dimensionless"
  ),
  stringsAsFactors = FALSE
)

kbl(glossary,
    booktabs = TRUE,
    format = "latex",
    escape = FALSE,
    longtable = TRUE,
    caption = "Glossary of terms and parameters used in the SS3 krill stock assessment model.",
    col.names = c("Symbol", "Description", "Units")) %>%
  kable_styling(latex_options = c("repeat_header", "HOLD_position"),
                font_size = 9,
                full_width = TRUE) %>%
  column_spec(1, width = "2.5cm") %>%
  column_spec(2, width = "9cm") %>%
  column_spec(3, width = "3cm")
```

\newpage

```{r echo=TRUE}
sessionInfo()
```


\newpage

# References

Methot, R.D. and Wetzel, C.R. (2013). Stock Synthesis: A biological and statistical framework for fish stock assessment and fishery management. *Fisheries Research*, 142: 86–99.

NMFS-OST (2025). *Stock Synthesis User Manual Version 3.30.23.2*. Available at: https://nmfs-ost.github.io/ss3-doc/SS330_User_Manual_release.html
